---
title: "TikTok Video View Summary"
format: html
---

# Goal

We summarize the `video_view` table from the SQLite database and check one question:
Do short videos keep the audience better than long ones?

# Load and inspect

```{r}
library(tidyverse)
library(here)
library(DBI)
library(RSQLite)

# load the video_view table from the SQLite database
con <- dbConnect(SQLite(), here("Data", "tiktok_students.sqlite"))
videos <- dbReadTable(con, "video_view")
dbDisconnect(con)

glimpse(videos)
```
```

# Overall numbers

```{r}
# one row with the totals and averages of the whole dataset
overview <- videos %>%
  summarise(
    n_videos       = n(),
    n_creators     = n_distinct(creator_id),
    avg_length     = mean(video_length_sec, na.rm = TRUE),
    avg_watch_rate = mean(watch_rate, na.rm = TRUE)
  )

overview
```

# Top creators

```{r}
# group per creator, then sort by total impressions
creator_summary <- videos %>%
  group_by(creator_id) %>%
  summarise(
    videos_n          = n(),
    impressions_total = sum(impressions_n, na.rm = TRUE),
    watch_rate_avg    = mean(watch_rate, na.rm = TRUE)
  ) %>%
  arrange(desc(impressions_total))

head(creator_summary, 5)
```

# Short videos vs long videos

```{r}
# make a group variable, then compare the two groups
length_groups <- videos %>%
  mutate(length_group = ifelse(video_length_sec < 30, "short", "long")) %>%
  group_by(length_group) %>%
  summarise(
    videos_n       = n(),
    watch_rate_avg = mean(watch_rate, na.rm = TRUE),
    watch_share_avg = mean(avg_watch_share, na.rm = TRUE)
  )

length_groups
```

# Conclusion

- The dataset is split almost evenly: slightly more long videos (≥ 30 sec) than short ones.
- Short and long videos have nearly the same watch rate and watch share.
- So in this data, video length does not clearly affect how well a video keeps its audience.