---
title: "TikTok Video View Summary"
format: html
---

# Goal

We summarize `video_view.csv` and check one question:
do short videos keep the audience better than long ones?

# Load and inspect

```{r}
library(tidyverse)

# download the data if it is not in the repo yet
data_file <- "../Data/raw/video_view.csv"

if (!file.exists(data_file)) {
  data_url <- paste0(
    "https://raw.githubusercontent.com/hannesdatta/course-dprep/",
    "refs/heads/main/material/project/video_view.csv"
  )
  download.file(data_url, data_file)
}

videos <- read_csv(data_file)

glimpse(videos)
```

# Overall numbers

```{r}
# one row with the totals and averages of the whole dataset
overview <- videos %>%
  summarise(
    n_videos       = n(),
    n_creators     = n_distinct(creator_id),
    avg_length     = mean(video_length_sec, na.rm = TRUE),
    avg_watch_rate = mean(watch_rate, na.rm = TRUE)
  )

overview
```

# Top creators

```{r}
# group per creator, then sort by total impressions
creator_summary <- videos %>%
  group_by(creator_id) %>%
  summarise(
    videos_n          = n(),
    impressions_total = sum(impressions_n, na.rm = TRUE),
    watch_rate_avg    = mean(watch_rate, na.rm = TRUE)
  ) %>%
  arrange(desc(impressions_total))

head(creator_summary, 5)
```

# Short videos vs long videos

```{r}
# make a group variable, then compare the two groups
length_groups <- videos %>%
  mutate(length_group = ifelse(video_length_sec < 30, "short", "long")) %>%
  group_by(length_group) %>%
  summarise(
    videos_n       = n(),
    watch_rate_avg = mean(watch_rate, na.rm = TRUE),
    watch_share_avg = mean(avg_watch_share, na.rm = TRUE)
  )

length_groups
```

# Conclusion

- Most videos in the dataset are short.
- Short videos have a higher average watch share: people finish them more often.
- Long videos still get watched, but viewers drop out before the end.